Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-21 Manuscript/manuscript.tex
Tackling easy Reviewer comments

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
% \usepackage{lineno}
% \usepackage{hyperref}
\usepackage{graphicx}

@@

A similar range of strategies, from random to near-optimal, has been found by Irons and Leber \citeyear{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm. This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (Figure \ref{fig:exampleStimuli}). The target is a defined as a red or blue box containing one of four numerals (e.g., 2-5), and on each trial one target of each colour is present. The participant's task is to find one of either target as quickly as possible and report the numeral. On trials in which the fourth colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters. As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target. The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours. Further work \cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.

@@

Another example of differences in search strategy comes from the foraging literature  \cite{kristjansson2014,johannesson2016}. In this context, foraging tasks involve searching for multiple targets on each trial. Participants were asked to search through a set of items from four categories, with two categories classed as targets. In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category. This strategy has previously been observed in animal foraging  \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates. However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with no cost to performance. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day mindfulness retreat on cognitive performance \cite{hartkamp2017}. From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.

Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes. \cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty. Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}.

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. This was verified in \cite{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture). There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The dominant eye position was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

@@

We would like to thanks Anna Nowakowska, {\'A}rn Kristj{\'a}nsson and Ian Thornton for sharing data and their helpful comments and suggestions. We would like to thank Charles Rigitano and Jacqueline Von Seth who helped with data collection. We acknowledge the funding support of the James S. McDonnell Foundation (Scholar Award to ARH) and NSF BCS-1632296 to ABL.

>>>>

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
% \usepackage{lineno}
% \usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

@@

A similar range of strategies, from random to near-optimal, has been found by Irons and Leber \citeyear{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm. This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (Figure \ref{fig:exampleStimuli}). The target is a defined as a red or blue box containing one of four numerals (e.g., 2-5), and on each trial one target of each colour is present. The participant's task is to find one of either target as quickly as possible and report the numeral. On trials in which the fourth colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters. As the fourth colour changes through purple to blue, participants should update their strategy and search for the red target. The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours. Further work \cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.

@@

Another example of differences in search strategy comes from the foraging literature  \cite{kristjansson2014,johannesson2016}. In this context, foraging tasks involve searching for multiple targets on each trial. Participants were asked to search through a set of items from four categories, with two categories classed as targets. In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category. This strategy has previously been observed in animal foraging  \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates. However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with \textcolor{blue}{very little} cost to performance. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day mindfulness retreat on cognitive performance \cite{hartkamp2017}. From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.

\textcolor{red} {Insert discussion of \cite{woods2013} here?}

Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometric measures, but to date, these differences have not shown strong correlations with other attributes. \cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty. Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}. \textcolor{blue}{However, there is evidence of a link between Attention Deficit/Hyperactivity Disorder and various search behaviours \cite{vandendriessche2019}.}

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. This was verified in \cite{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture. There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The dominant eye position was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

@@

We would like to thanks Anna Nowakowska, {\'A}rni Kristj{\'a}nsson and Ian Thornton for sharing data and their helpful comments and suggestions. We would like to thank Charles Rigitano and Jacqueline Von Seth who helped with data collection. We acknowledge the funding support of the James S. McDonnell Foundation (Scholar Award to ARH) and NSF BCS-1632296 to ABL.
